---
title: "Week 7: Tidy Data and Data Wrangling"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(readr)
```

## The dataset
First read in the data set which is available at: [http://www.math.montana.edu/ahoegh/teaching/stat408/datasets/BaltimoreTowing.csv](http://www.math.montana.edu/ahoegh/teaching/stat408/datasets/BaltimoreTowing.csv).
```{r, message = F}
baltimore.tow <- 
  read_csv('http://www.math.montana.edu/ahoegh/teaching/stat408/datasets/BaltimoreTowing.csv')
str(baltimore.tow)
```

## Motivating Exercise: group_by()

Now compute the average towing cost grouped by month.

## Exercise: Using the substr() function
Use the substr() function to extract month and create a new variable in R. 

## Exercise: Using the strsplit() function
Use the strsplit() function to remove the dollar sign from the cost.


## Exercise: Stringr approach
Use the `stringr` package to remove (replace) the dollar sign. Note that a dollar sign is a special character, so you'll need to use `\\$`.

## Exercise: Delete Misc. Type Vehicles

First we will delete golf carts, boats, and trailers. There are several ways to do this, consider making a new data frame called balt.tow.small that does not include golf carts, boats, and trailers.


## Exercise: Create Additional Groups

Now we need to create a variable for the additional groups below.

1. Cars - (Car, convertible)
2. Large Cars - (SUV, Station Wagon, Sport Utility Vehicle, Van, Taxi)
3. Trucks - (Pick-up Truck, Pickup Truck)
4. Large Trucks - (Truck, Tractor Trailer, Tow Truck, Tractor, Construction Equipment, Commercial Truck)
5. Bikes - (Motor Cycle (Street Bike), Dirt Bike, All terrain - 4 wheel bike, Mini-Bike)

